Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-06-13 ms.tex
Some minor changes

The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs. The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess. The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.  Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively.

\section{Results}
No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS.

A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background. Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean of zero and unit standard deviation. The results are listed in Table \ref{table:results}.

>>>>

The ring background model \citep{article:Aharonian_etal:2001} is used to estimate the background due to CRs. The total number of events in a given region of interest is then compared to the estimated background from the off-source region scaled by the ratio of the solid angles to produce a final excess. The VHE gamma-ray significance is then calculated using the method by \citet{article:LiMa:1983}.  Significance skymaps over the VERITAS field of view are shown in Figure \ref{fig:skymaps} with overlaid X-ray and radio contours from the ROSAT all-sky survey \citep{article:BrielHenryBohringer:1992}  and GBT 1.4 GHz observations \citep{article:BrownRudnick:2010} respectively. The skymaps were produced with a $0.2^{\circ}$ sampling radius.

\section{Results}
No significant excess of VHE gamma-rays from the Coma cluster was detected with VERITAS, as illustrated by the $\theta^{2}$ distribution shown in  Figure \ref{fig:thetasq}. The $\theta^{2}$ distribution is a radial comparison of the ON-source event distribution with the estimated background. A 99\% confidence level upper limit is calculated for each region of interest using the method described by \citet{article:Rolke:2005} assuming a Gaussian background. Figure \ref{fig:sigdist} shows that the VERITAS data is well fit by a Gaussian with a mean close to zero and a standard deviation within a few percent of unity. The results are listed in Table \ref{table:results}.
